ROV report

### 2020-03-24 analysis/reports/rov.Rmd
scruffy but extant

>>>>

```{r map of percentiles}
ggplot(all_di, aes(log(s0), log(n0), color = skew_percentile)) +
  geom_point(alpha = .3) +
  theme_bw() +
  scale_color_viridis_c(limits = c(0, 100))
ggplot(all_di, aes(log(s0), log(n0), color = simpson_percentile)) +
  geom_point(alpha = .2) +
  theme_bw() +
  scale_color_viridis_c(limits = c(0, 100))
